Active learning for efficient systematic reviews

### 2020-06-18 manuscript/manuscript/Ferdinands, G - MSBBSS.Rmd
first draft simulation study documentation

datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts. The Wilson dataset [@Appenzeller-Herzog2020] - from the field of _medicine_ - is on a review on the effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019]. From the same scientific field, the Ace dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006]. From _virology_, the Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020]. From the field of _software engineering_, the Software dataset contains publications from a review on fault prediction in source code [@Hall2012]. The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of _behavioural public administration_. The PTSD dataset contains publications from the field of _psychology_. The corresponding systematic review is on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017]. Of these six datasets, Ace, and Software have been used for model simulations in previous studies on ML-aided title and abstract screening, respectively [@Cohen2006] and [@Yu2018].

@@

\begin{center}
`r table_nums("datasets")` 
\end{center}
```{r, results = 'asis'}
datastats <- datastats %>%
  select(dataset, candidates_test, incl_test, inclrate_test) 
colnames(datastats) <- c("dataset", rep(c("Candidate publications", 
                                       #"Studies selected for fulltext screening", 
                                       "Relevant publications", 
                                       "Inclusion rate (%)"),1))
datastats <- datastats[c(2,3,4,1,5,6), ]
print(xtable(datastats, digits = c(0,0,0,0,1)),
      include.rownames=FALSE, comment = FALSE, booktabs = TRUE,
      format.args = list(big.mark = ",", decimal.mark = "."))
```

@@

@@

tabwss95 <- rbind(tabwss95, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))
# insert N per dataset

@@

tabrrf10 <- rbind(tabrrf10, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))

>>>>

Datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts. The Wilson dataset [@Appenzeller-Herzog2020] - from the field of _medicine_ - is on a review on the effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019]. From the same scientific field, the Ace dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006]. From _virology_, the Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020]. From the field of _software engineering_, the Software dataset contains publications from a review on fault prediction in source code [@Hall2012]. The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of _behavioural public administration_. The PTSD dataset contains publications from the field of _psychology_. The corresponding systematic review is on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017]. Of these six datasets, Ace, and Software have been used for model simulations in previous studies on ML-aided title and abstract screening, respectively [@Cohen2006] and [@Yu2018].

@@

\begin{center}
`r table_nums("datasets")` 
\end{center}
```{r, results = 'asis'}
datastats <- datastats %>%
  select(dataset, candidates_test, incl_test, inclrate_test) 
colnames(datastats) <- c("dataset", rep(c("Candidate publications", 
                                       #"Studies selected for fulltext screening", 
                                       "Relevant publications", 
                                       "Inclusion rate (%)"),1))
datastats <- datastats[c(2,3,4,1,5,6), ]
saveRDS(datastats, "tables/tab1_data.RDS")

print(xtable(datastats, digits = c(0,0,0,0,1)),
      include.rownames=FALSE, comment = FALSE, booktabs = TRUE,
      format.args = list(big.mark = ",", decimal.mark = "."))
```

@@

saveRDS(tabatd, file = "tables/tab2_atd.RDS")

@@

tabwss95 <- rbind(tabwss95, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))
# insert N per dataset 
saveRDS(tabwss95, file = "tables/tab3_wss95.RDS")

@@

tabrrf10 <- rbind(tabrrf10, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))
saveRDS(tabrrf10, file = "tables/tab4_rrf10.RDS")
